% Preamble
\input{src/cv/preamble}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
    {\HUGE\textcolor{black}{\textbf{Pol}}} % First name

	{\HUGE\textcolor{black}{\textbf{Dellaiera}}} % Last name
    \vspace{6pt}

	{\huge Research, analysis, development} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{\href{https://www.openstreetmap.org/\#map=15/50.5969/4.3228}{Nivelles}}\\
	\icon{At}{12}{\href{mailto:pol.dellaiera@protonmail.com}{pol.dellaiera@protonmail.com}}\\
	\icon{Globe}{12}{\href{https://not-a-number.io}{not-a-number.io}}\\
\end{minipage}
\begin{minipage}[t]{0.20\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{https://github.com/loophp}{github.com/loophp}}\\
	\icon{Github}{12}{\href{https://github.com/drupol}{github.com/drupol}}\\
	\icon{Twitter}{12}{\href{https://twitter.com/@drupol}{@drupol}}\\
\end{minipage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{About}

\begin{minipage}[t]{.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
    \justify{
    I have been working with web development since 2010, the period during which
    I have worked in different environments, from start-ups to consultancy
    companies.
    \\\\I am a self-motivated and self-taught professional who likes solving
    problems.
    \\\\Perpertual student, curious, meticulous, I appreciate the beauty of
    simple, natural and efficient solutions.
    }
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.57\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{6}
		\baritem{PHP}{100}
		\baritem{Linux/FreeBSD/Gentoo/NixOS}{95}
        \baritem{\textbf{O}bject \textbf{O}riented \textbf{P}rogramming}{90}
        \baritem{\textbf{F}unctional \textbf{P}rogramming}{90}
		\baritem{Git}{85}
		\baritem{Algorithm}{85}
		\baritem{Docker}{75}
		\baritem{LaTeX}{65}
	\end{barchart}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{7/2019 -- present}
        {Full time}
		{Software engineer}
        {European Commission}
        {
			Hired under the behalf of a consultancy company as a software engineer consultant.

			Working at \href{https://ec.europa.eu/info/departments/informatics_en}{Digit} B.4 (\textit{Software Engineering Capabilities}),
			in charge of building a PHP competency center.

			In that team, I'm responsible for helping clients migrating from ColdFusion to PHP, providing help,
			custom bundle and packages, custom assistance and short-terms consultancy missions.
			\\ \texttt{Nix}\slashsep\texttt{Symfony}\slashsep\texttt{Doctrine}\slashsep\texttt{API Platform}\slashsep\texttt{Oracle}\slashsep\texttt{Docker}\slashsep\texttt{InfrastructureAsCode}
        }
	\entry
		{6/2015 -- 6/2019}
        {Full time}
		{Software engineer}
        {European Commission}
        {
			Hired under the behalf of a consultancy company as a software engineer consultant.

			Working at \href{https://ec.europa.eu/info/departments/informatics_en}{Digit} D.3 (Digital services),
			on the NextEuropa and OpenEuropa platforms running respectively Drupal 7 and 8.
			\\ \texttt{PHP}\slashsep\texttt{Drupal}\slashsep\texttt{MariaDB}\slashsep\texttt{Docker}
        }
    \entry
        {\color{black!50}Before 6/2015}
        {}
        {}
        {}
        {\footnotesize{\color{black!50}This is the public and short version of my CV. Please ask the full version if needed by sending an \href{mailto:pol.dellaiera@protonmail.com}{email}.}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{.48\textwidth}
	\cvsect{Education}

	\begin{entrylist}
		\entry
			{\tiny{2001 -- 2005}}
            {Distinction}
			{Bachelor's Degree}
            {\href{https://www.heh.be/}{Haute Ecoles en Hainaut}}
			{IT and systems, specialization in network and telecommunications}
	\end{entrylist}

	\begin{entrylist}
		\entry
			{\tiny{2018 -- 2021}}
            {}
			{Music theory}
            {\href{https://academiedenivelles.be/}{Académie de musique de Nivelles}}
			{Musical instrument: piano}
	\end{entrylist}
\end{minipage}
\hfill
\begin{minipage}[t]{.48\textwidth}
	\cvsect{Certificates}

	\begin{entrylist}
		\entry
			{01/2020}
            {}
			{Certificate}
			{The Linux Foundation}
			{\href{https://courses.edx.org/certificates/01fdb9d9242546e8bc45153468dfd785}{Blockchain: Understanding Its Uses and Implications}}
	\end{entrylist}

	\begin{entrylist}
		\entry
			{09/2015}
            {}
			{Certificate}
			{Acquia}
			{\href{https://certification.acquia.com/user/249}{Acquia Certified Developer}}
	\end{entrylist}

	\begin{entrylist}
		\entry
			{09/2015}
            {}
			{Certificate}
			{Acquia}
			{\href{https://certification.acquia.com/user/249}{Acquia Certified Back End Specialist}}
	\end{entrylist}
\end{minipage}


%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{.2\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{French} - native\\
	\textbf{Anglais} - proficient\\
	\textbf{Italian} - proficient\\
	\textbf{Dutch} - rudimentary\\
\end{minipage}
\hfill
\begin{minipage}[t]{.45\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Hobbies}

    Besides my work and the geek stuff, I’m currently fulfilling a childhood dream, I’m learning music and piano!
    I love photography and I learned by myself most of the secrets of a reflex camera, just for fun.
    I swim a lot and I also really like riding my mountain bike.
\end{minipage}
\hfill
\begin{minipage}[t]{.30\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Non profit}

    Contributor in many open-source projects, especially in PHP, Symfony and Drupal.

    I'm also an OpenStreetMap user and contributor.
\end{minipage}
\hfill
\begin{minipage}[t]{\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Favorite quotes}

    \begin{itemize}
        \item "Simplicity is the ultimate sophistication."{\tiny{---Leonardo Da Vinci}}
        \item "Only when the last tree has been cut down, the last fish been caught, and the last stream poisoned, will we realize we cannot eat money."{\tiny{---Indian author}}
        \item "We may regard the present state of the universe as the effect of its past and the cause of its future. An intellect which at any given moment knew all of the forces that animate nature and the mutual positions of the beings that compose it, if this intellect were vast enough to submit the data to analysis, could condense into a single formula the movement of the greatest bodies of the universe and that of the lightest atom; for such an intellect nothing could be uncertain and the future just like the past would be present before its eyes."{\tiny{---Pierre Simon de Laplace}}
    \end{itemize}
\end{minipage}

%----------------------------------------------------------------------------------------

\null
\vspace*{\fill}

\noindent{\color{black!15}\rule{\textwidth}{.5pt}}

\makebox[\linewidth][r]{
    \color{black!50}
    \tiny{
        Public version
        $\cdot$
        \href{https://github.com/drupol/cv/commit/\gitrevisionlong}{\faIcon{code-branch} {\gitrevisionsmall}}
    }
}

\end{document}
